### 2015-11-26 pfpl/cheatsheet.tex
Add new files Add .gitignore Create sort branch
Remove sort
First cut at some contents to see if this is the right direction.

\documentclass[12pt]{article}
\usepackage[margin=.5in]{geometry}
\begin{document}
\begin{tabular}[b] {p{.1\textwidth} p{.15\textwidth} p{.22\textwidth} p{.4\textwidth}}
Expression & Name & Say & Meaning \\ \\
$\mathcal{P}$ & Script P & Proposition & Something to be proved \\
$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$

>>>>

\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{proof}
\usepackage{hyperref}

\usepackage[margin=.5in]{geometry}
\begin{document}
\begin{tabular}[b] {p{.1\textwidth} p{.15\textwidth} p{.22\textwidth} p{.4\textwidth}}
Expression & Name & Say & Meaning \\ \\
$\mathcal{P}$ & Script P & Proposition & Something to be proved \\
$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$ \\
$\mathcal{O}$ & Script O & Operator & An operator that can be used in an AST \\
$\mathcal{O}(\it{a})$ & Script O of $\it{a}$ & Operator of arity $\it{a}$ & An operator of a given arity \\
$\mathcal{X}_{\it{s}}$ & Script X sub s & Variable $\it{x}$ of sort $\it{s}$ & A variable x of sort s \\
$\{ X _{s} \} _{\it{s} \in \mathcal{S}}$  & Family & Set X of s & a sort-indexed family of disjoint finite sets X s of variables x of sort s
